Paper

### 2020-01-07 Paper_resubmit.Rmd
...

kmp = survminer::ggsurvplot(sfit, size=1, linetype="strata",risk.table=T, risk.table.col='strata',
                      conf.int=T, censor=T, legend='none', title='Risks over time', xlab='Time (months prior to final sample)',
                      ylab = 'Progression risk',
                      ggtheme=theme_minimal(), palette=as.vector(BarrettsProgressionRisk::riskColors()), font.legend=c(14,'bold'))

@@

kmp = survminer::ggsurvplot(sfit, size=1, linetype="strata",risk.table=T, risk.table.col='strata',
                      conf.int=T, censor=T, legend='none', 
                      title='Risks over time', 
                      subtitle='Training & Validation predictions',
                      xlab='Time (months prior to final sample)',
                      ylab = 'Progression risk',
                      ggtheme=theme_minimal(), palette=as.vector(BarrettsProgressionRisk::riskColors()), font.legend=c(14,'bold'))

@@

## Check COX

@@

```{r}
cache.dir = '~/Data/BarrettsProgressionRisk/Analysis/models_5e6_all/supp_train_n/insilico_splits/'

purrr::map(list.files(cache.dir, 'loo.Rdata',recursive = T, full.names = T), function(f) {
  load(f,verbose=T)

  length(unique(pg.samp$Patient))

}

>>>>

kmp = survminer::ggsurvplot(sfit, size=1, linetype="strata",risk.table=T, risk.table.col='strata',
                      conf.int=T, censor=T, legend='none', title='Risks over time', xlab='Time (months prior to final sample)',
                      ylab = 'Progression risk',
                      ggtheme=theme_minimal(), palette=unlist(BarrettsProgressionRisk::riskColors()), font.legend=c(14,'bold'))

@@

kmp = survminer::ggsurvplot(sfit, size=1, linetype="strata",risk.table=T, risk.table.col='strata',
                      conf.int=T, censor=T, legend='none', 
                      title='Risks over time', 
                      subtitle='Training & Validation predictions',
                      xlab='Time (months prior to final sample)',
                      ylab = 'Progression risk',
                      ggtheme=theme_minimal(), palette=unlist(BarrettsProgressionRisk::riskColors()), font.legend=c(14,'bold'))

@@

# Check COX

@@

```{r, fig.width=12, fig.height=8}
model.dir = '~/Data/BarrettsProgressionRisk/Analysis/models_5e6_all/50kb/'
load(list.files(model.dir, 'loo_0.9.Rdata',recursive = T, full.names = T))
d.n.patient = length(unique(pg.samp$Patient))
d.roc = pROC::roc(Status ~ Prediction, data = pg.samp, ci=T, of='thresholds', transpose=T)

load(list.files(model.dir, 'all.pt.alpha',recursive = T, full.names = T))
d.coefs = coefs[['0.9']]
d.perf = performance.at.1se[['0.9']]$mean
rm(dysplasia.df, plots, pg.samp, models, nzcoefs, fits, performance.at.1se)

all.dir = '~/Data/BarrettsProgressionRisk/Analysis/dv_model_5e6_all_dvz/50kb/'
load(list.files(all.dir, 'loo_0.9.Rdata',recursive = T, full.names = T))
dv.n.patient = length(unique(pg.samp$Patient))
dv.n.samples = length(unique(pg.samp$Samplename))
dv.roc = pROC::roc(Status ~ Probability, data = pg.samp, ci=T, of='thresholds', transpose=T)

load(list.files(all.dir, 'all.pt.alpha',recursive = T, full.names = T))
dv.coefs = coefs[['0.9']]
dv.perf = performance.at.1se[['0.9']]$mean
rm(dysplasia.df, plots, pg.samp, models, nzcoefs, models, performance.at.1se)

cache.dir = '~/Data/BarrettsProgressionRisk/Analysis/models_5e6_all/'
filenames = list.files(cache.dir, 'supp*')

info = do.call(bind_rows, purrr::map(list.files(cache.dir, 'merged.Rdata', recursive = T, full.names = T), function(f) {
  load(f,verbose=F)
  model.info
})) %>% mutate('Cohort' = 'Discovery (patient subsets)')

info = add_row(info, n.patients = d.n.patient, cv.performance = d.perf, n.coefs = nrow(d.coefs), n.samples = 773, auc = d.roc$auc, Cohort = 'Discovery (all)')

info = add_row(info, n.patients = dv.n.patient, cv.performance = dv.perf, n.coefs = nrow(dv.coefs), n.samples = dv.n.samples, auc = dv.roc$auc, Cohort = 'Discovery+Validation')

x = info %>% group_by(n.patients, Cohort) %>% dplyr::summarise_at(vars(-n.samples), list(~mean(.), ~sd(.))) %>% as_tibble %>% mutate(n.patients = factor(n.patients), Cohort = factor(Cohort, levels=c('Discovery (patient subsets)', 'Discovery (all)', 'Discovery+Validation'), ordered=T))

p = ggplot(x, aes(x=n.patients, y=cv.performance_mean, group=n.patients, fill=Cohort)) + 
  facet_grid(~Cohort, scales = 'free_x', space='free_x') + 
  geom_col() + geom_errorbar(aes(ymin=cv.performance_mean-cv.performance_sd/2, ymax=cv.performance_mean+cv.performance_sd/2), width=0.2, color='grey39') +
  geom_text(aes(label=round(cv.performance_mean,2)), y=0.05) + 
  scale_y_continuous(expand=c(0,0), limits=c(0,0.8)) + 
  scale_fill_brewer(palette = 'Set2',name='') + 
  plot.theme + theme(legend.position = 'bottom', strip.text = element_blank(), panel.spacing = unit(0.5, 'lines')) +
  labs(title='Cross validation performance', y='mean', x='# patients used to train')

legend = get_legend(p)
p = p + theme(legend.position = 'none')

p1 = ggplot(x, aes(x=n.patients, y=n.coefs_mean, group=n.patients, fill=Cohort)) + 
  facet_grid(~Cohort, scales = 'free_x', space='free_x') + 
  geom_col() + geom_errorbar(aes(ymin=n.coefs_mean-n.coefs_sd/2, ymax=n.coefs_mean+n.coefs_sd/2), width=0.2, color='grey39') +
  geom_text(aes(label=round(n.coefs_mean,2)), y=5) +
  scale_y_continuous(expand=c(0,0), limits=c(0,125)) + scale_fill_brewer(palette = 'Set2') + 
  plot.theme + theme(legend.position = 'none', strip.text = element_blank(), panel.spacing = unit(0.5, 'lines')) +
  labs(title='# Coefficients',y='mean', x='# patients used to train')

p2 = ggplot(x, aes(x=n.patients, y=auc_mean, group=n.patients, fill=Cohort)) +
  facet_grid(~Cohort, scales = 'free_x', space='free_x') + 
  geom_col() + geom_errorbar(aes(ymin=auc_mean-auc_sd/2, ymax=auc_mean+auc_sd/2), width=0.2, color='grey39') +
  geom_text(aes(label=round(auc_mean,2)), y=0.05) +
  scale_y_continuous(expand=c(0,0), limits=c(0,1)) + scale_fill_brewer(palette = 'Set2') + 
  plot.theme + theme(legend.position = 'none', strip.text = element_blank(), panel.spacing = unit(0.5, 'lines')) +
  labs(title='AUC', y='mean', x='# patients used to train')

grid.arrange(arrangeGrob(p,p1,p2,nrow=1), arrangeGrob(legend), heights=c(4,1))

ggsave(filename='plots/performance/training_n_pts.png',
       plot=grid.arrange(arrangeGrob(p,p1,p2,nrow=1), arrangeGrob(legend), heights=c(4,1)), width=12, height=8, units='in', dpi=300)
